Viscous Erosion in Porous Media

### 2018-03-13 docs/methods/erosion_methods.tex
NM

We further quantify many of these observations in Fig.~\ref{fig:mbodyplots}. First, Fig.~\ref{fig:mbodyplots}(a) shows area fraction versus time. The area fraction is the total area of all bodies as compared to the domain area, i.e.~the 2D counterpart of volume fraction. The initial configuration of 6 circles comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode. Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time. Since we have fixed the pressure drop across the cell in these simulations, $\umax$ steadily increases as the bodies diminish and provide less resistance. Here, the vertical axis is logarithmic, and so the plot suggests exponential increase of $\umax$ at early times. This rapid increase in flow is likely due to the erosion-induced channelization observed above. In Fig.~\ref{fig:mbodyplots}(c) we show the total drag, summed over all bodies, versus time. Though the bodies diminish due to erosion, the steady increase of $\umax$ causes the total drag to remain relatively constant. Only near the end of the simulation does the drag decrease rapidly to zero. To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the total drag scaled on $\umax$. This value is a measure for the aggregate {\em resistance} of all bodies. Due to linearity of the Stokes equations, this measure does not depend on the flow-rate $\umax$, only on the bodies and their configuration. As seen here, the resistance decreases rapidly as the bodies erode. Accounting for the logarithmic vertical axis suggests an exponential decrease in resistance at early times, which is likely connected to the channelization process.

>>>>

We further quantify many of these observations in Fig.~\ref{fig:mbodyplots}. First, Fig.~\ref{fig:mbodyplots}(a) shows area fraction versus time. The area fraction is the total area of all bodies as compared to the domain area, i.e.~the 2D counterpart of volume fraction. The initial configuration of 6 circles comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode. Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time. Since we have fixed the pressure drop across the cell in these simulations, $\umax$ steadily increases as the bodies diminish and provide less resistance. Here, the vertical axis is logarithmic, and so the plot suggests exponential increase of $\umax$ at early times. This rapid increase in flow is likely due to the erosion-induced channelization observed above. In Fig.~\ref{fig:mbodyplots}(c) we show the total drag, summed over all bodies, versus time. Though the bodies diminish due to erosion, the steady increase of $\umax$ causes the total drag to remain relatively constant. Only near the end of the simulation does the drag decrease rapidly to zero. To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the total drag scaled on $\umax$. This value is a measure for the aggregate {\em resistance} of all bodies. Due to linearity of the Stokes equations, this measure does not depend on the flow-rate $\umax$, only on the bodies and their configuration. As seen here, the resistance decreases rapidly as the bodies erode. Since the vertical axis is logarithmic, the plot suggests an exponential decrease in resistance at early times, which is likely connected to the channelization process.
